---
title: "Economic variables and TB percentage reported"
output: html_notebook
---

Aim: To look at the relationship between various socioeconomic variables (GDP, secondary school enrolment, rural population as percentage of total population, adolescent population as percentage of total population)

STEP 1: Load the data 
```{r}
setwd("~/Desktop/AFP/TB MODELLING 2/Resource Factors")
gdp <- read_csv("gdp_percapita.csv", skip = 4)
health_exp1 <- read_csv("gov_health_2015_2018.csv", skip = 4)
health_exp2 <- read_csv("dom_gov_health_2015_2018.csv")
schl_pop <- read_csv("data_bank.csv")
```

STEP 2: Refining GDP data

```{r}
colnames(gdp)
gdp1 <- gdp[, c(1,2, 60:65)]
colnames(gdp1)[colnames(gdp1) == "Country Code"] <- "iso3"
merge_gdp <- merge(bigdata_TB, gdp1, by = "iso3", all.x = TRUE)
merge_gdp <- merge_gdp[, -39]
colnames(merge_gdp)[colnames(merge_gdp) == "2015"] <- "gdp_2015"
colnames(merge_gdp)[colnames(merge_gdp) == "2016"] <- "gdp_2016"
colnames(merge_gdp)[colnames(merge_gdp) == "2017"] <- "gdp_2017"
colnames(merge_gdp)[colnames(merge_gdp) == "2018"] <- "gdp_2018"
colnames(merge_gdp)[colnames(merge_gdp) == "2019"] <- "gdp_2019"
colnames(merge_gdp)[colnames(merge_gdp) == "2020"] <- "gdp_2020"
merge_gdp$perc_tot014[merge_gdp$perc_tot014 == Inf] <- NA 
merge_gdp$perc_tot014[merge_gdp$gdp_2019 == Inf] <- NA 


#Regression with GDP
mod_gdp <- lm(merge_gdp$perc_tot014 ~ merge_gdp$gdp_2019)
summary(mod_gdp)

plot(x = merge_gdp$gdp_2019, y = merge_gdp$perc_tot014, xlab = "gdp_2019", ylab = "perc_tot014")
abline(mod_gdp, col = "red", lwd = 2)

```
STEP 3: Refining the school enrollment data

```{r}
unique(schl_pop$`Series Name`)
schl_enrol <- filter(schl_pop, schl_pop$`Series Name` == "School enrollment, secondary (% net)")
schl_enrol <- schl_enrol[, -c(1:2)]
schl_enrol[schl_enrol == ".."] <- NA
colnames(schl_enrol)[colnames(schl_enrol) == "2018 [YR2018]"] <- "schl_2018"
colnames(schl_enrol)[colnames(schl_enrol) == "Country Code"] <- "iso3"
schl_gdp <- merge(merge_gdp, schl_enrol, by = "iso3", all.x = TRUE)
schl_gdp <- schl_gdp[, -c(45:48, 50:51)]
schl_gdp$schl_2018 <- as.numeric(schl_gdp$schl_2018)

#Creating a regression analysis with school attendance 
mod_schl <- lm(schl_gdp$perc_tot014 ~ schl_gdp$schl_2018)
summary(mod_schl)

plot(schl_gdp$schl_2018, schl_gdp$perc_tot014, xlab = "schl_enrolment", ylab = "perc_tot_014")
abline(mod_schl, col = "red", lwd = 2)

```
STEP 4: Refining data for percentage rural population

```{r}
rural_pop <- filter(schl_pop, schl_pop$`Series Name` == "Rural population (% of total population)")
rural_pop <- rural_pop[, -c(1,2)]
colnames(rural_pop) <- c("Country", "iso3", "rural_2015", "rural_2016", "rural_2017", "rural_2018", "rural_2019", "rural_2020")
rural_tb <- merge(schl_gdp, rural_pop, by = "iso3", all.x = TRUE)
rural_tb <- rural_tb[, -46]
rural_tb$rural_2019 <- as.numeric(rural_tb$rural_2019)

#Regression with rural population percentage in 2019
mod_rural <- lm(rural_tb$perc_tot014 ~ rural_tb$rural_2019)
summary(mod_rural)

plot(x = rural_tb$rural_2019, y = rural_tb$perc_tot014, xlab = "rural_2019", ylab = "perc_tot014")
abline(mod_rural, col = "red", lwd = 2)
```

STEP 5: Refining data on undernourishment 

```{r}
under5 <- filter(schl_pop, schl_pop$`Series Name` == "Mortality rate, under-5 (per 1,000)")
under5 <- under5[, -c(1:2)]
colnames(under5) <- c("Country", "iso3", "mort5_2015", "mort5_2016", "mort5_2017", "mort5_2018", "mort5_2019", "mort5_2020")
under5$mort5_2019 <- as.numeric(under5$mort5_2019)
under5[under5 == ".."] <- NA
under5_tb <- merge(rural_tb, under5, by = "iso3", all.x = TRUE)
under5_tb <- under5_tb[, -52]

#Regression analysis with under 5 mortality 
under5_tb$perc_tot04[under5_tb$perc_tot04 == Inf] <- NA
mod_under5 <- lm(under5_tb$perc_tot04 ~ under5_tb$mort5_2019)
summary(mod_under5)

plot(x = under5_tb$mort5_2019, y = under5_tb$perc_tot04, xlab = "mort5_2019", ylab = "perc_tot04")
abline(mod_under5, col = "red", lwd = 2)

```

